---
title: "strings factors"
author: "nz2333"
date: "10/29/2021"
output: github_document
---
```{r}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, "m")
str_replace(string_vec, "jeff", "Jeff")
```
*detect is "m" is in there. case sensitive!
*replace jeff with Jeff. 


```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "^i think")
str_detect(string_vec, "i think$")
```
* ^:beginning of the line
  $:end of the line

```{r}
string_vec = c(
  "Y'all remember Pres. HW Bush?",
  "I saw a green bush",
  "BBQ and Bushwalking at Molonglo Gorge",
  "BUSH -- LIVE IN CONCERT!!"
  )

str_detect(string_vec,"[Bb]ush")
```
*[Bb]:upper or lower case

```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")
```
*number followed by two letters. 

```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
```
* anything between 7 and 11. 

```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]'
  )

str_detect(string_vec, "\\[")
```
*actually trying to find [, not a range. 


## Why factors are weird
```{r}
factor_vec = factor(c("male", "male", "female", "female"))
as.numeric(factor_vec)

factor_vec = fct_relevel(factor_vec, "male")
as.numeric(factor_vec)
```


## NSDUH
```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

table_marj = 
  read_html(nsduh_url) %>%
  html_table() %>%
  first()%>%
  slice(-1)
```

clean data set
```{r}
marj_df = 
table_marj %>%
  select(-contains("P Value")) %>%
  pivot_longer(-State, 
               names_to = "age_year", 
               values_to = "percent") %>%
  separate(age_year, into = c("age", "year"), "\\(") %>%
  mutate(
    year = str_replace(year, "\\)", ""),
  percent = str_replace(percent, "[a-c]$", ""), 
  percent = as.numeric(percent)
  ) %>%
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
```
*!: unselect

Do dataframe stuff
```{r}
marj_df %>%
  filter(age == "12-17") %>%
  mutate(
    State = fct_reorder(State, percent)
  ) %>%
  ggplot(aes(x = State, y = percent, color = year)) +
  geom_point() +
  theme(axis.text.x=element_text(angle=90, vjust = 0.5, hjust = 1))
```
* mutate: reorder State in the order of percent


## Restaurant Inspections
```{r}
library(p8105.datasets)
data("rest_inspec")
```

```{r}
rest_inspec %>%
  group_by(boro, grade) %>%
  summarize(count = n())

rest_inspec %>%
  janitor::tabyl(boro, grade)
```

```{r}
rest_inspec =
  rest_inspec %>%
  filter(
    str_detect(grade, "[ABC]"), 
    !(boro == "Missing")
  ) %>%
  mutate(boro = str_to_title(boro))
```
*mutate: all capital letters changed to first one cap, rest lower case. 

```{r}
rest_inspec %>%
  filter(str_detect(dba, "Pizza")) %>%
  janitor::tabyl(boro, grade)


rest_inspec %>%
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>%
  janitor::tabyl(boro, grade)
```

```{r}
rest_inspec %>%
    filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>%
  mutate(
    boro = fct_infreq(boro)
  ) %>%
    ggplot(aes(x = boro, fill = grade)) +
  geom_bar() +
  facet_grid(.~grade)
```

Changing factor labels
```{r}
rest_inspec %>%
    filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>%
  mutate(
    boro = fct_infreq(boro), 
    boro = fct_recode(boro, "The City" = "Manhattan")
  ) %>%
    ggplot(aes(x = boro, fill = grade)) +
  geom_bar()
```
* Replaced one of the label to Manhattan from The City


